### 2021-06-14 papers/thesis/full/ch1-introduction/introduction.tex
Added comments/questions
Addressed final points. Removed comments.

One could say this is surprising, given that there is a long history of around 150 years associated with multivariate OPs, beginning with Hermite first presenting the multivariate Hermite polynomials in 1865 \cite{appel1926fonctions, ismail2017review}. Zernike polynomials \cite{zernike1934diffraction} were first introduced in 1934, as another example, that are a group of bivariate polynomials orthogonal on a unit circle. Koornwinder in 1975 described a method for constructing two-variable OPs from univariate OPs \cite{koornwinder1975two}. However, few books have been published over the years on the topic of multivariate orthogonal polynomials, with the notable exception of the book by Dunkl \& Xu \cite{dunkl2014orthogonal}. As Dumitriu, Edelman and Shuman said in 2007, \enquote{\textit{[multivariate orthogonal polynomials] are understudied, underapplied, and important applications may be being missed}} \cite{dumitriu2007mops}, while in 2016, Olver opined that \enquote{\textit{there is still a long way to go before multivariate orthogonal polynomials can reach their full potential in applications}}. He hypothesised that \enquote{\textit{[p]art of this neglect may be due to the fact that mutually orthogonal polynomials are not uniquely defined: there is no canonical ordering}} and continued \enquote{\textit{[e]ven when explicit constructions are known, these are often unwieldy}} \cite{olver2016review}.

>>>>

One could say this is surprising, given that there is a long history of around 150 years associated with multivariate OPs, beginning with Hermite first presenting the multivariate Hermite polynomials in 1865 \cite{appel1926fonctions, ismail2017review}. Zernike polynomials \cite{zernike1934diffraction} were first introduced in 1934, as another example, that are a group of bivariate polynomials orthogonal on a unit circle. Koornwinder in 1975 described a method for constructing two-variable OPs from univariate OPs \cite{koornwinder1975two}. However, few books have been published over the years on the topic of multivariate orthogonal polynomials, with the notable exception of the book by Dunkl \& Xu \cite{dunkl2014orthogonal}. As Dumitriu, Edelman and Shuman said in 2007, \enquote{[multivariate orthogonal polynomials] are understudied, underapplied, and important applications may be being missed} \cite{dumitriu2007mops}, while in 2016, Olver opined that \enquote{there is still a long way to go before multivariate orthogonal polynomials can reach their full potential in applications}. He hypothesised that \enquote{[p]art of this neglect may be due to the fact that mutually orthogonal polynomials are not uniquely defined: there is no canonical ordering} and continued \enquote{[e]ven when explicit constructions are known, these are often unwieldy} \cite{olver2016review}.

### 2021-06-14 papers/thesis/full/foreword/foreword.tex
Added comments/questions
Addressed final points. Removed comments.

\item The contents of \bsrefchapter{CHAPTER:sphericalcaps} has been accepted for publication in \textit{Transactions of Mathematics and Its Applications}:

>>>>

\item The contents of \bsrefchapter{CHAPTER:sphericalcaps} has been submitted for publication in \textit{Transactions of Mathematics and Its Applications}:
